---
title: "Disparities in Patient Portal Access by US Adults (HINTS 2020)"
author: "Akira Nishii"
date: "07/08/2022"
output: html_document
---

## Load Library and data

```{r setup, include=TRUE, message=FALSE}
knitr::opts_chunk$set(echo =TRUE)

library(haven)
library(tidyverse); theme_set(theme_bw())
library(tigerstats)
library(SmartEDA)
library(caret)
library(Hmisc)
library(lsr)
library(base)
library(survey)
library(data.table)
library(metaviz)
library(corrplot)
library(rlang)
library(purrr)
# library(ggforestplot)

```

```{r}

data <- read_sas("hints5_cycle4_public.sas7bdat")

```

## Extract relevant data

```{r}

select_data <- data %>% select(FreqGoProvider, HealthInsurance, AccessOnlineRecord, NotAccessed_SpeakDirectly, NotAccessed_NoInternet, NotAccessed_NoNeed, NotAccessed_ConcernedPrivacy, NotAccessed_NoRecord, NotAccessed_LogInProb, NotAccessed_Uncomfortable, NotAccessed_MultipleRec, RaceEthn5, Age, BirthGender, EducA, Occupation_Employed, RUC2013, HealthIns_InsuranceEmp, HealthIns_InsurancePriv, HealthIns_Medicare, HealthIns_Medicaid, HealthIns_Tricare, HealthIns_VA, HealthIns_IHS, HealthIns_Other, HHInc, RegularProvider, QualityCare, GeneralHealth, Pandemic, OfferedAccessHCP2, OfferedAccessInsurer2,WhereUseInternet_Home, UseInternet, c(PERSON_FINWT1:PERSON_FINWT0))

```

## Clean variables

```{r}

#Rename pandemic variable
select_data$Pandemic <- as.factor(select_data$Pandemic)

select_data <- select_data %>% 
  mutate(Pandemic = recode(.x = Pandemic, "-1" = "Before", "1" = "After"))

#Create the combined health insurance variable 
#Fill in InsuranceType variable (do other first, then private, then medicare, then medicaid)

select_data$InsuranceType <- NA
select_data$InsuranceType[select_data$HealthIns_Tricare == "1"] <- "Other"
select_data$InsuranceType[select_data$HealthIns_VA == "1"] <- "Other"
select_data$InsuranceType[select_data$HealthIns_IHS == "1"] <- "Other"
select_data$InsuranceType[select_data$HealthIns_Other == "1"] <- "Other"
select_data$InsuranceType[select_data$HealthIns_InsuranceEmp == "1"] <- "Private"
select_data$InsuranceType[select_data$HealthIns_InsurancePriv == "1"] <- "Private"
select_data$InsuranceType[select_data$HealthIns_Medicare == "1"] <- "Medicare"
select_data$InsuranceType[select_data$HealthIns_Medicaid == "1"] <- "Medicaid"

```

```{r}

#Create the Offered Access Variable
#Set all NA is equal to -5
select_data$OfferedAccessHCP2[select_data$OfferedAccessHCP2 == "-9"] <- "-5"
select_data$OfferedAccessInsurer2[select_data$OfferedAccessInsurer2 == "-9"] <- "-5"

#Make all "No", then add "Yes" and "NA"
select_data$OfferedAccess <- "No"
select_data$OfferedAccess[select_data$OfferedAccessHCP2 == "1"] <- "Yes"
select_data$OfferedAccess[select_data$OfferedAccessInsurer2 == "1"] <- "Yes"
select_data$OfferedAccess[select_data$OfferedAccessInsurer2 == "-5" & select_data$OfferedAccessHCP2 == "-5"] <- NA

```

```{r}

#Make NA
nalist <- c(-2, -4, -6, -9, -1, -5)

for(i in nalist) {
  select_data[select_data == i] <- NA
}

#Make the NAs in Race and Income "Missing"
select_data$RaceEthn5[is.na(select_data$RaceEthn5)] <- "Missing"
select_data$HHInc[is.na(select_data$HHInc)] <- "Missing"

```

```{r}

#Convert num into factor

cols <- c("FreqGoProvider", "HealthInsurance", "AccessOnlineRecord", "NotAccessed_SpeakDirectly", "NotAccessed_NoInternet", "NotAccessed_NoNeed", "NotAccessed_ConcernedPrivacy", "NotAccessed_NoRecord", "NotAccessed_LogInProb", "NotAccessed_Uncomfortable", "NotAccessed_MultipleRec", "RaceEthn5", "BirthGender", "EducA", "Occupation_Employed", "RUC2013", "InsuranceType", "RegularProvider", "GeneralHealth", "Pandemic", "OfferedAccess","WhereUseInternet_Home", "UseInternet", "HHInc")

select_data[,cols] <- lapply(select_data[,cols],as.factor)

```


```{r}

setDT(select_data, keep.rownames = TRUE)[]
clean <- select_data

```

```{r}

#Rename variables

clean <- clean  %>% mutate(AccessOnlineRecord = dplyr::recode(.x = AccessOnlineRecord, "0" = "No", "1" = "Yes", "2" = "Yes", "3" = "Yes", "4" = "Yes")) %>% 
  mutate(NotAccessed_SpeakDirectly = dplyr::recode(.x = NotAccessed_SpeakDirectly, "1" = "Yes", "2" = "No"))%>% 
  mutate(NotAccessed_NoInternet = dplyr::recode(.x = NotAccessed_NoInternet, "1" = "Yes", "2" = "No")) %>% 
  mutate(NotAccessed_NoNeed = dplyr::recode(.x = NotAccessed_NoNeed, "1" = "Yes", "2" = "No")) %>% 
  mutate(NotAccessed_ConcernedPrivacy = dplyr::recode(.x = NotAccessed_ConcernedPrivacy, "1" = "Yes", "2" = "No")) %>% 
  mutate(NotAccessed_NoRecord = dplyr::recode(.x = NotAccessed_NoRecord, "1" = "Yes", "2" = "No")) %>% 
  mutate(NotAccessed_LogInProb = dplyr::recode(.x = NotAccessed_LogInProb, "1" = "Yes", "2" = "No")) %>% 
  mutate(NotAccessed_Uncomfortable = dplyr::recode(.x = NotAccessed_Uncomfortable, "1" = "Yes", "2" = "No")) %>% 
  mutate(NotAccessed_MultipleRec = dplyr::recode(.x = NotAccessed_MultipleRec, "1" = "Yes", "2" = "No")) %>% 
  mutate(RaceEthn5 = dplyr::recode(.x = RaceEthn5, "1" = "Non-Hispanic White", "2" = "Non-Hispanic Black", "3" = "Hispanic","4" = "Other","5" = "Other")) %>% 
  mutate(BirthGender = dplyr::recode(.x = BirthGender, "1" = "Male", "2" = "Female")) %>% 
  mutate(EducA = recode(.x = EducA, "1" = "High School or Less", "2" = "High School or Less", "3" = "Some College","4" = "College Graduate or More")) %>% 
  mutate(Occupation_Employed = dplyr::recode(.x = Occupation_Employed, "1" = "Employed", "2" = "Not Employed")) %>% 
  mutate(RUC2013 = dplyr::recode(.x = RUC2013, "1" = "Metro", "2" = "Metro", "3" = "Metro", "4" = "Nonmetro","5" = "Nonmetro", "6" = "Nonmetro","7" = "Nonmetro", "8" = "Nonmetro")) %>% 
  mutate(RegularProvider = dplyr::recode(.x = RegularProvider, "1" = "Yes", "2" = "No")) %>%
  mutate(QualityCare = dplyr::recode(.x = QualityCare, "1" = "5", "2" = "4", "3" = "3", "4" = "2", "5" = "1"))%>%
  mutate(GeneralHealth = dplyr::recode(.x = GeneralHealth, "1" = "Excellent, Very good, Good", "2" = "Excellent, Very good, Good", "3" = "Excellent, Very good, Good", "4" = "Fair, Poor", "5" = "Fair, Poor"))  %>% 
  mutate(UseInternet = dplyr::recode(.x = UseInternet, "1" = "Yes", "2" = "No")) %>% 
  mutate(HHInc = dplyr::recode(.x = HHInc, "1" = "<$35,000", "2" = "<$35,000",
                               "3" = "$35-$74,999","4" = "$35-$74,999", "5" = "$75,000+"))

#Make age category
clean <- clean %>% mutate(age_cat = case_when(Age >= 18 & Age <= 30 ~ '18-30',
                                              Age >= 31 & Age <= 40 ~ '31-40',
                                              Age >= 41 & Age <= 50 ~ '41-50',
                                              Age >= 51 & Age <= 64 ~ '51-64',
                                              Age >= 65 ~ '65 or older'))

clean$age_cat <- as.factor(clean$age_cat)

#WE'RE USING USE INTERNET INSTEAD! Make the two variables interchangable so I don't make any errors later when running regressions
clean$WhereUseInternet_Home <- clean$UseInternet

```


```{r}

clean$QualityCare <- as.numeric(clean$QualityCare)
write.csv(clean, file = "clean_data.csv", row.names = FALSE)

```

```{r}

#relevel data
clean <- clean %>% 
  mutate(NotAccessed_SpeakDirectly = fct_relevel(NotAccessed_SpeakDirectly, 
                                   c("No", 
                                     "Yes"))) %>% 
  mutate(NotAccessed_NoInternet = fct_relevel(NotAccessed_NoInternet, 
                                   c("No", 
                                     "Yes"))) %>% 
  mutate(NotAccessed_NoNeed = fct_relevel(NotAccessed_NoNeed, 
                                   c("No", 
                                     "Yes"))) %>% 
  mutate(NotAccessed_ConcernedPrivacy = fct_relevel(NotAccessed_ConcernedPrivacy, 
                                   c("No", 
                                     "Yes"))) %>% 
  mutate(NotAccessed_NoRecord = fct_relevel(NotAccessed_NoRecord, 
                                   c("No", 
                                     "Yes"))) %>% 
  mutate(NotAccessed_LogInProb = fct_relevel(NotAccessed_LogInProb, 
                                   c("No", 
                                     "Yes"))) %>% 
  mutate(NotAccessed_Uncomfortable = fct_relevel(NotAccessed_Uncomfortable, 
                                   c("No", 
                                     "Yes"))) %>% 
  mutate(NotAccessed_MultipleRec = fct_relevel(NotAccessed_MultipleRec, 
                                   c("No", 
                                     "Yes"))) %>% 
  mutate(BirthGender = fct_relevel(BirthGender, 
                                   c("Male", 
                                     "Female"))) %>% 
  mutate(EducA = fct_relevel(EducA, 
                                   c("College Graduate or More", 
                                     "Some College",
                                     "High School or Less"))) %>% 
  mutate(Occupation_Employed = fct_relevel(Occupation_Employed, 
                                   c("Employed", 
                                     "Not Employed"))) %>% 
  mutate(InsuranceType = fct_relevel(InsuranceType, 
                                   c("Private", 
                                     "Medicaid",
                                     "Medicare",
                                     "Other")))  %>%
  mutate(age_cat = fct_relevel(age_cat, 
                                   c("18-30",
                                     "31-40",
                                     "41-50",
                                     "51-64",
                                     "65 or older")))

```

## Test for multicollinearity

```{r}

# test for correlation of covariates
# source: https://towardsdatascience.com/how-to-create-a-correlation-matrix-with-too-many-variables-309cc0c0a57

select_data_corr <- clean %>% select(RaceEthn5, age_cat, BirthGender, EducA, Occupation_Employed, RUC2013, InsuranceType, RegularProvider, QualityCare, GeneralHealth, Pandemic, WhereUseInternet_Home)

# Convert all values into numeric
# source: https://www.geeksforgeeks.org/convert-factor-to-numeric-and-numeric-to-factor-in-r-programming/#:~:text=vector%20using%20as.-,numeric().,factor%20levels%20will%20be%20returned.

select_data_corr <- select_data_corr %>% mutate_if(is.character, as.factor)
select_data_corr <- select_data_corr %>% mutate_if(is.factor, as.numeric)

#Run correlation
selectdata.corr <- rcorr(as.matrix(select_data_corr))
selectdata.coeff <- selectdata.corr$r
selectdata.p <- selectdata.corr$P

#Filter correlations
#prepare to drop duplicates and correlations of 1     
selectdata.coeff[lower.tri(selectdata.coeff,diag=TRUE)] <- NA 
#drop perfect correlations
selectdata.coeff[selectdata.coeff == 1] <- NA 

#Create dataframes from matrix
selectdata.coeffdf <- as.data.frame(as.table(selectdata.coeff))
selectdata.pdf <- as.data.frame(as.table(selectdata.p))

#Rename column names
selectdata.coeffdf <- selectdata.coeffdf  %>% rename(corr = Freq)
selectdata.pdf <- selectdata.pdf  %>% rename(p = Freq)

#Create dataframe with both coeff and p values
selectdata.coeffpdf <- merge(selectdata.coeffdf, selectdata.pdf)

#select significant values  
selectdata.coeffpdf <- na.omit(selectdata.coeffpdf)
selectdata.coeffpdf <- subset(selectdata.coeffpdf, p < 0.05) 
#sort by highest correlation
selectdata.coeffpdf <- selectdata.coeffpdf %>% arrange(p)

#turn corr back into matrix in order to plot with corrplot
mtx_corr <- reshape2::acast(selectdata.coeffpdf, Var1~Var2, value.var="corr")
  
#plot correlations visually
corrplot(mtx_corr, is.corr=FALSE, tl.col="black", na.label=" ")

```


##  Table 1 (unweighted)

```{r}

table1vars <- c("AccessOnlineRecord", "OfferedAccess","RaceEthn5", "age_cat", "BirthGender", "EducA", "Occupation_Employed", "RUC2013", "RegularProvider", "QualityCare", "GeneralHealth", "InsuranceType", "FreqGoProvider", "HealthInsurance", "Pandemic", "WhereUseInternet_Home")

```

```{r}

table_gen <- function(data) {
  
  check <- data %>% select(all_of(table1vars))

  setDT(check)

  check <- na.omit(check, col = table1vars)

  check <- subset(check, FreqGoProvider != 0)
  check <- subset(check, HealthInsurance != 2)
  
  return(check)
  
}
  
  
```

### Table1 values for Yes to Offered Access

```{r}

check <- table_gen(clean)
check <- subset(check, OfferedAccess == "Yes")
summary(check)

```


```{r}

mean(check$QualityCare)
sd(check$QualityCare)

```

### Table1 values for No to Offered Access


```{r}

check <- table_gen(clean)
check <- subset(check, OfferedAccess == "No")
summary(check)

```

```{r}

mean(check$QualityCare)
sd(check$QualityCare)

```

### Table1 values (all)

```{r}


check <- table_gen(clean)
summary(check)

```


```{r}

mean(check$QualityCare)
sd(check$QualityCare)

```


## Table 1 (weighted)

### Take care of FreqGoProvider and HealthInsurance Variables first

```{r}

#read in labels
label <- read.csv("label.csv")

clean$subset_var <- as.numeric(clean$subset_var)

#create a variable that will later contain 1s where there is no NAs in the row
clean$subset_var <- 1

############### This section takes care of FreqGoProvider ######################

#Set subset_var to 0 when FreqGoProvider is 0 or NA
clean$subset_var[clean$FreqGoProvider == 0] <- 0
clean$subset_var[is.na(clean$FreqGoProvider)] <- 0

############### This section takes care of HealthInsurance ######################

#Set subset_var to 0 when HealthInsurance is 2 or NA
clean$subset_var[clean$HealthInsurance == 2] <- 0
clean$subset_var[is.na(clean$HealthInsurance)] <- 0

```

### Functions for removing NAs based on different independent variables (offered = Yes)

```{r}

### Function to remove na for all variables of interst

include_pandemic <- function(ind, clean_ = clean) {
  
  #Create new dataframe only containing variables of interest and rows with NA in them
  data_na <- clean_ %>% select(rn, {{ind}}, AccessOnlineRecord, OfferedAccess, RaceEthn5, age_cat, BirthGender, EducA, Occupation_Employed, RUC2013, RegularProvider, QualityCare, GeneralHealth, Pandemic, InsuranceType, WhereUseInternet_Home)

  summary(data_na)

  data_na <- data_na[!complete.cases(data_na), ]

  #Set subset_var to 0s where there are NAs in the row
  clean_[match(data_na$rn, clean_$rn), which(colnames(clean_)=="subset_var")] <- 0

  #Check number of 0s and 1s
  clean_$subset_var <- as.factor(clean_$subset_var)
  clean_ %>% select(subset_var) %>% summary()
  
  #Data preparaton and survey design for replicate weighting
  select_data_dsgn<-svrepdesign(data=clean_,repweights=select(clean_, PERSON_FINWT1:PERSON_FINWT50), type="JKn", combined.weights=TRUE, weights=clean_$PERSON_FINWT0,scale=1,rscales=0.98)

  #Data subsetting

  dsub <- subset(select_data_dsgn, subset_var == 1)
  
  return(dsub)
}

### Function for getting table from the model

weightedtable <- function(model) {
  
  tbl_svysummary(
  {{model}},
  digits = list(all_categorical() ~ c(0, 1)),
  include = table1vars)
  
}

```

### Table 1 Incorporating Survey Weights (offered = Yes)

```{r}

library(gtsummary)
# source: https://www.danieldsjoberg.com/gtsummary/reference/tbl_svysummary.html

newdf <- clean
#MODIFY THIS VARIABLE JUST FOR THE TABLE
newdf$subset_var[newdf$OfferedAccess == "No"] <- 0

dsub <- include_pandemic(AccessOnlineRecord, newdf)
weightedtable(dsub)


```

```{r}

svymean(~QualityCare, dsub)

```

### Table 1 Incorporating Survey Weights (offered = No)

```{r}

newdf <- clean
#MODIFY THIS VARIABLE JUST FOR THE TABLE
newdf$subset_var[newdf$OfferedAccess == "Yes"] <- 0
dsub <- include_pandemic(AccessOnlineRecord, newdf)
weightedtable(dsub)

```

```{r}

svymean(~QualityCare, dsub)

```

### Table 1 Incorporating Survey Weights (all data)

```{r}

dsub <- include_pandemic(AccessOnlineRecord, clean)
weightedtable(dsub)

```

```{r}

svymean(~QualityCare, dsub)

```

### Table 1 statistics

```{r message=FALSE}

table1statsvars <- c("AccessOnlineRecord","RaceEthn5", "age_cat", "BirthGender", "EducA", "Occupation_Employed", "RUC2013", "RegularProvider", "QualityCare", "GeneralHealth", "InsuranceType", "Pandemic", "WhereUseInternet_Home")

library(car)
dsub <- include_pandemic(OfferedAccess, clean)

table1stats <- function(var, dsn = dsub) {
  f <- substitute(svyglm(OfferedAccess ~ var, data = clean_, family = "quasibinomial", design = dsn))
  Anova(eval(f),2)
}

```

```{r}

for(i in table1statsvars) {
  i <- rlang::sym(i)
  f <- expr(table1stats(!!i, dsub))
  print(eval(f))
}

```

## Logistic regression models

### AccessOnlineRecord (include pandemic variable)

```{r}

run_model <- function(dv, df = clean, dsn = dsub, str = "") {
  
  f <- substitute(svyglm(dv ~ RaceEthn5 + age_cat + BirthGender + EducA + Occupation_Employed + RUC2013 + RegularProvider + QualityCare + GeneralHealth + Pandemic + InsuranceType + WhereUseInternet_Home, data = df, family = "binomial", design = dsn))
  svyglm_model <- eval(f)
  print(summary(svyglm_model))
  print(car::vif(svyglm_model))
  
  #This section gets odds ratios
  print("Odds ratio")
  #get odds ratio
  or <- exp(svyglm_model$coefficients[-1])
  print(or)
  
  print("Odds ratio as percentages")
  #get odds ratio at percentage
  print((exp(svyglm_model$coefficients[-1])-1)*100)
  or <- as.data.frame(or)

  ci <- exp(confint(svyglm_model))[-1,]
  or <- merge(or, ci, by=0, all=TRUE)

  #remove whitespace
  or$Row.names <- gsub('\\s+', '', or$Row.names)

  #reorder the entire table
  ordering <- read.csv("order.csv")
  order_vector <- as.vector(ordering$order)
  or <- or[match(order_vector, or$Row.names),]

  #rename columns to remove whitespace
  or <- or %>% dplyr::rename_all(list(~make.names(.)))
  
  fileloc <- paste0("odds_ratios/odds_ratios_", as_string(enexpr(dv)), str, ".csv")
  write.csv(or, fileloc)
  
  #log odds ratios
  or <- svyglm_model$coefficients[-1]
  se <- summary(svyglm_model)$coefficients[-1, c(2,4)]
  or <- as.data.frame(or)
  se <- as.data.frame(se)

  or <- merge(or, se, by=0, all=TRUE)


  #remove whitespace
  or$Row.names <- gsub('\\s+', '', or$Row.names)

  #reorder the entire table
  ordering <- read.csv("order.csv")
  order_vector <- as.vector(ordering$order)
  or <- or[match(order_vector, or$Row.names),]

  #rename columns to remove whitespace
  or <- or %>% dplyr::rename_all(list(~make.names(.)))

  fileloc <- paste0("log_odds_ratios/log_odds_ratios_", as_string(enexpr(dv)), str, ".csv")
  write.csv(or, fileloc)
}


```

```{r warning=FALSE}

dsub <- include_pandemic(AccessOnlineRecord)
run_model(AccessOnlineRecord)

```


### OfferedAccess (include pandemic variable)

```{r warning=FALSE}

dsub <- include_pandemic(OfferedAccess)
run_model(OfferedAccess)

```


## Table 3

### Reasons for non-access ("No" for AccessOnlineRecord)

```{r warning=FALSE}

reasons <- c("NotAccessed_ConcernedPrivacy", "NotAccessed_SpeakDirectly", "NotAccessed_NoInternet", "NotAccessed_NoNeed", "NotAccessed_NoRecord", "NotAccessed_LogInProb", "NotAccessed_Uncomfortable","NotAccessed_MultipleRec")

newdf <- clean
newdf$subset_var[newdf$AccessOnlineRecord == "Yes"] <- 0

for(i in reasons) {
  i <- rlang::sym(i)
  dsub <- eval(expr(include_pandemic(!!i, newdf)))
  eval(expr(run_model(!!i)))
}
```


## Figure (plots)

Plots were commented out because the new version of R does not support ggforestplot (uncomment and run on older version of R to get the plots)

<!-- ```{R} -->

<!-- plot_data <- read.csv("ggforest.csv") -->

<!-- labels.vec <- c("Uncomfortable with technology", "Concerned about privacy", "Prefers direct communication", "Perceived not needed", "Inability to access website", "No online record") -->
<!-- plot_data <- plot_data %>% -->
<!--   mutate(reason = fct_relevel(reason, labels.vec)) -->

<!-- age <- plot_data %>% filter(variable == "Age") -->
<!-- sex <- plot_data %>% filter(variable == "Sex") -->
<!-- race <- plot_data %>% filter(variable == "Race") -->
<!-- educ <- plot_data %>% filter(variable == "Education") -->
<!-- emp <- plot_data %>% filter(variable == "Employment") -->
<!-- loc <- plot_data %>% filter(variable == "Location") -->
<!-- gh <- plot_data %>% filter(variable == "General Health") -->
<!-- ins <- plot_data %>% filter(variable == "Insurance type") -->
<!-- rp <- plot_data %>% filter(variable == "Regular Provider") -->
<!-- int <- plot_data %>% filter(variable == "Use Internet") -->
<!-- qc <- plot_data %>% filter(variable == "Quality Care") -->


<!-- ggforestplot::forestplot( -->
<!--   df = age, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "Age (ref: 18-30)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=25)) -->


<!-- ``` -->

<!-- ```{R} -->

<!-- #To get legend -->
<!-- ggforestplot::forestplot( -->
<!--   df = sex, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "Sex (ref: male)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(text = element_text(size=17))  -->


<!-- ``` -->

<!-- ```{R} -->

<!-- #For plot without legend -->
<!-- ggforestplot::forestplot( -->
<!--   df = sex, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "Sex (ref: male)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=20))  -->


<!-- ``` -->


<!-- ```{R} -->

<!-- ggforestplot::forestplot( -->
<!--   df = race, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "Race/ethnicity\n(ref: non-Hispanic white)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=20))  -->


<!-- ``` -->

<!-- ```{R} -->

<!-- ggforestplot::forestplot( -->
<!--   df = educ, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "Education\n(ref: college or more)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=20))  -->


<!-- ``` -->


<!-- ```{R} -->

<!-- ggforestplot::forestplot( -->
<!--   df = emp, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "Employment status (ref: employed)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=20)) -->


<!-- ``` -->


<!-- ```{R} -->

<!-- ggforestplot::forestplot( -->
<!--   df = loc, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "Location (ref: metro)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=20)) -->


<!-- ``` -->

<!-- ```{R} -->

<!-- ggforestplot::forestplot( -->
<!--   df = gh, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "General Health\n(ref: Excellent, Very good, Good)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=20)) -->


<!-- ``` -->

<!-- ```{R} -->

<!-- ggforestplot::forestplot( -->
<!--   df = ins, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "Insurance type (ref: private)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=20)) -->


<!-- ``` -->

<!-- ```{R} -->

<!-- ggforestplot::forestplot( -->
<!--   df = rp, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "Has a regular health care provider\n(ref: yes)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=20)) -->


<!-- ``` -->

<!-- ```{R} -->

<!-- ggforestplot::forestplot( -->
<!--   df = int, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "Use internet (ref: yes)", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=20)) -->


<!-- ``` -->

<!-- ```{R} -->

<!-- ggforestplot::forestplot( -->
<!--   df = qc, -->
<!--   name = characteristic, -->
<!--   estimate = or, -->
<!--   se = se, -->
<!--   pvalue = pvalue, -->
<!--   psignif = 0.05, -->
<!--   colour = reason, -->
<!--   xlab = "Odds ratio", -->
<!--   title = "QualityCare", -->
<!--   logodds = TRUE -->
<!-- ) + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none") + theme(text = element_text(size=20)) -->


<!-- ``` -->